{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-07 Paper/main.tex
Additional Simulation Code

	The parameter $M$ corresponds to the chosen number of principal components and therefore constitutes another choice in the approximation. Using only $M$ functional principal components therefore leads to the following approximation.
	\begin{equation}
		y_i \approx \tilde{\alpha}^L
		+ \sum_{m = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} {\color{red}\sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s} \right] + \epsilon_i 
		= \tilde{\alpha}^L
		+ \sum_{m = 1}^{M} \tilde{\xi}^{m,L}_{i} {\color{red}\bar{b}^{m,L}} + \epsilon_i
	\end{equation}

	As in the previous section, this equation again lends itself for estimation with OLS. Define the following objects:
	\begin{equation}
		Y = \begin{pmatrix}
			y_1 \\ \vdots \\ y_n
		\end{pmatrix}, \quad
		Z = \begin{pmatrix}
			1 & \tilde{\xi}^{1,L}_{1} & \dots & \tilde{\xi}^{M,L}_{1} \\
			\vdots & \vdots & \ddots & \vdots \\
			1 & \tilde{\xi}^{1,L}_{N} & \dots & \tilde{\xi}^{M,L}_{N}
		\end{pmatrix}
	\end{equation}

@@

	\newpage
	\section{Definition and Proofs}
	\cite{alexanderian_KLexpansion_2015} was referred for the following definitions and proofs.

>>>>

	The parameter $M \in \{1, \dots, N-1\}$ corresponds to the chosen number of principal components and therefore constitutes another choice in the approximation. Using only $M$ functional principal components therefore leads to the following approximation.
	\begin{equation}
		y_i \approx \tilde{\alpha}^L
		+ \sum_{m = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} {\color{red}\sum_{j = 1}^{L} b_j \int_{0}^{1} \tilde{\nu}^{m,L}(s) \phi_j(s) \mathrm{d}s} \right] + \epsilon_i 
		= \tilde{\alpha}^L
		+ \sum_{m = 1}^{M} \tilde{\xi}^{m,L}_{i} {\color{red}\bar{b}^{m,L}} + \epsilon_i
	\end{equation}

	As in the previous section, this equation lends itself for estimation with OLS and we can define the following objects.
	\begin{equation}
		Y = \begin{pmatrix}
			y_1 \\ \vdots \\ y_n
		\end{pmatrix}, \quad
		Z = \begin{pmatrix}
			1 & \tilde{\xi}^{1,L}_{1} & \dots & \tilde{\xi}^{M,L}_{1} \\
			\vdots & \vdots & \ddots & \vdots \\
			1 & \tilde{\xi}^{1,L}_{N} & \dots & \tilde{\xi}^{M,L}_{N}
		\end{pmatrix}
	\end{equation}

@@

	\newpage
	\section{Definitions and Proofs}
	\cite{alexanderian_KLexpansion_2015} was referred for the following definitions and proofs.
